---
title: "chronophile_comment_conceptual_fig"
author: "Drew Steen"
format: gfm
editor: visual
---

```{r setup, message=FALSE}
library(tidyverse)
theme_set(theme_classic())
```

I'm taking data from the Bar-On paper about relative abundance of microbes (and animals, etc) in different environments: Bar-On et al 2018 PNAS.

Bar-On get \~10\^26 "microbiome" (i.e., host-associated) cells, and \~10\^30 total microbial cells (see their supplmenetal information, top of page 61.)

Thus, the total number of host-associated cells is \~0.01% of the 'environmental' cells.

# Power vs doubling time

I feel like power is inversely related to doubling time when all else is held constant. Can't really justify that mathematically but I feel it in my heart.

```{r, message=FALSE}
log.td <- seq(0, 5, length.out = 1000)
td <- 10^log.td
power <- 1/td
d <- tibble(log.td, td, power)

p <- ggplot(d, aes(x=log.td, y=power)) + 
  geom_line() +
  scale_y_log10() +
  xlab(expression(paste(log[10], "(doubling time, hr)")))
print(p)
```
